Evolution of Methodologies in Delivering Reliable Software in the European Scientific Arena

### 2018-06-04 paper-ieee-trans.tex
Add exact values for code coverage.

\item \textit{Unit and Functional testing}.
Changes involving the addition of new functionalities, are required to be tested. \textit{Regression
testing} in this context is accomplished by enforcing the definition and periodic execution
of the tests, covering past fixed issues, to ensure that they are not reintroduced during the development activities.

%% Comment from reviewer
%% These percentages appear as vague approximations by eye, please add the precise numbers rounded.

 \textit{Unit testing} completes the source code testing evaluation by
focusing on the code's internal design. The SQA criteria set a recommended threshold of
70\% coverage for unit testing. In Fig.~\ref{fig:fig_unittest}, unit testing coverage is compared
for each software component between the two major {\sl INDIGO--DataCloud} releases, denoting an incremental
trend over the course of the project. It can be seen that 50\% of the components were over the
70\% threshold while slightly less than 80\% of the product stack had values over 50\% coverage.

>>>>

\item \textit{Unit and Functional testing}.
Changes involving the addition of new functionalities, are required to be tested. \textit{Regression
testing} in this context is accomplished by enforcing the definition and periodic execution
of the tests, covering past fixed issues, to ensure that they are not reintroduced during the development
activities. \textit{Unit testing} completes the source code testing evaluation by focusing on the code's 
internal design. The SQA criteria of {\sl INDIGO--DataCloud} set a recommended threshold of 70\% coverage 
for unit testing. In Fig.~\ref{fig:fig_unittest}, unit testing coverage is compared for each software 
component between the two major releases, denoting an incremental trend over the course of the project: 
code coverage increased from an average value of 50.32\% to 63.34\%, outlined by the respective dates of
the project's first (INDIGO-1) and second (INDIGO-2) releases. By INDIGO-2, half of the software components
(17 out of 32) were over the threshold of the aforementioned project's SQA code coverage recommendation 
(70\%), while three-quarters (24 out of 32) of the product stack exceeded 50\% coverage.
